Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-08-12 paper/paper.tex
Updates on amplitude modulation
Update intro paragraph

\affiliation{1}{
  Rosenstiel School of Marine, Atmospheric, and Earth Science,
  University of Miami,
  Miami, FL
}
\affiliation{2}{
  Frost Institute for Data Science and Computing,
  University of Miami,
  Miami, FL
}

@@

\begin{keypoints}
\item We revisit analytical and numerical solutions for hydrodynamic modulation of short waves by longer waves from linear wave theory.
\item We extend the original solution by \citeA{longuet1960changes} to a higher-order solution.
\item In contrast to earlier studies, we find that there exist stable numerical solutions for modulation by realistic long-wave groups.
\end{keypoints}

@@

\begin{equation}
\label{eq:tau}
\widetilde{k} = k (1 + a_L k_L)
\end{equation}
where $\widetilde{k}$ and $k$ are the modulated and unmodulated wavenumbers of
short waves, respectively, and $a_L$ and $k_L$ are amplitude and wavenumber
of the long wave, respectively.
This result has been influential on the development of remote sensing of ocean
surface waves and currents \cite{keller1975microwave,hara1994hydrodynamic}
and has been used even recently \cite{peureux2021unsteady} to simulate
unsteady growth of short-waves due to longer waves.

Working through the theory of \citeA{longuet1960changes,longuet1987propagation}
and the numerical simulation of \citeA{peureux2021unsteady}, I found several
gaps in the current understanding of the hydrodynamic modulation of short waves
based on linear wave theory that I thought were worth revisiting.

In this study, we extend the \citeA{longuet1960changes} theory (hereafter L-HS)
to a higher-order solution following the linear wave theory, and present revised
phase-averaged estimates of short-wave properties in presence of long waves.

\section{Governing equations}

@@

@@

\section{Conclusions}

>>>>

\affiliation{1}{
  Rosenstiel School of Marine, Atmospheric, and Earth Science,
  University of Miami,
  Miami, FL
}
\affiliation{2}{
  Frost Institute for Data Science and Computing,
  University of Miami,
  Coral Gables, FL
}

@@

\begin{keypoints}
\item We revisit analytical and numerical solutions for hydrodynamic modulation of short waves by longer waves.
\item We present a higher-order analytical solution based on linear wave theory.
\item In contrast to an earlier study, we find stable numerical solutions for modulation by realistic long-wave groups.
\end{keypoints}

@@

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
This result has been influential on the development of remote sensing of ocean
surface waves and currents \cite{keller1975microwave,hara1994hydrodynamic}.
\citeA{longuet1987propagation} revisited this problem by considering variation
in the gravitational acceleration and fully non-linear wave numerical solutions
to find significantly stronger modulation than that predicted by
Eq. \ref{eq:lhs1960wavenumber}.
\citeA{zhang1990evolution} evaluated the effects of nonlinearity of short waves
using a non-linear Schr\" odinger equation and found higher wavenumber
modulation but lesser amplitude modulation than those predicted by
\citeA{longuet1987propagation}.
More recently, \cite{peureux2021unsteady} simulated the full wave conservation
equations and found that the short waves grow unsteadily due to the propagation of
longer waves, suggesting that the steady-state solutions may only be valid for
a few long-wave periods before the short waves are steep enough to break.

In this paper, we revisit this problem from a linear wave theory perspective and
derive new non-linear solutions for the modulation of short waves, evaluated
at the long-wave surface.
We also perform numerical simulations of the full wave crest and action
conservation laws and evaluate the effect of long-wave groups on the short waves.
The next section presents the governing equations, followed by the analytical
solutions in section \ref{section:analytical_solutions}.
In section \ref{section:numerical_solutions} we present the numerical solutions
and compare them to the analytical solutions.
In section \ref{section:scale_analysis} we perform a scale analysis of the
analytical solutions to quantify the relative importance of the terms in the
full equation set.
Finally, we summarize the results and discuss their implications in section
\ref{section:conclusions}.

\section{Governing equations}
\label{section:governing_equations}

@@

\begin{figure}[h]
\label{fig:amplitude_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_amplitude_modulation_2panel.png}
\caption{
}
\end{figure}

@@

\section{Conclusions}
\label{section:conclusions}
